Adopting agile in the large: motivations, success factors and challenges

### 2014-04-25 journal/article.tex
Communication and collaboration issues

--> Demand of better customer collaboration

A few organizations were experiencing rise of agile methods at grass roots
level, but early use of agile resluted in problems when the organization used a
waterfall method on the top level. Tensions arose when teams using different
development approaches attempted to collaborate on products [P10]. On a team
level agile had enabled some flexibility, but that flexibility could not be
leveraged on the scale of the entire organization [P26]. This kind of
experiences drove the organization to deploy agile on a full scale.

%%%%%%%%%%%%%%

% ----------------------------------------------------------------

>>>>

Too little customer and user collaboration led to problems in some
organizations. For instance, too late user involvment led to change requests
late in the project [P40]. There was a wish to collaborate more frequently and
in less formal ways [P4, P26].

A few organizations were experiencing rise of agile methods at grass roots
level, but the agile teams could not collaborate efficiently with other parts of
a waterfall organization. Tensions arose when teams using different development
approaches attempted to work together on products [P10]. On a team level agile
had enabled some flexibility, but that flexibility could not be leveraged on the
scale of the entire organization [P26]. This kind of experiences drove the
organization to deploy agile on a full scale.
